Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-30 paper.tex
first pass at fixing contour problems
pp 408 of Morse and feshbach

An often unavoidable consequence in electronic spectroscopy is broadened line shapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
In the discussion that follows, we assume that a ground state vibrational frequency, $\ket{g,v}$, experiences variations that are correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,\tilde{v}'}$ is $\omega_{e\tilde{v}'} + c\xi$, where c is a shift coefficient.
We assume the fluctuations controlling the frequency variations are slow (the static limit), so that homogeneous lineshapes are unaffected by this fluctuation. 
When both states positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
For simplicity, we consider only c = $\pm$1.

@@

Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details.} 
\begin{subequations}
\begin{equation}\label{linenarrowa}
	\gamma_{ijkl} = \frac{- \eta_{ijkl}}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba} + \Delta_{ga}} \right)
\end{equation}
for correlated ($c = 1$) states and
\begin{equation}
	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
\end{equation}
\end{subequations}
for anti-correlated ($c = -1$) states.
The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
As such, the HDFG pathway considered in this work line-narrows correlated modes. 
These results are consistent with the idea that non-parametric, non-linear spectroscopies line-narrow correlated modes. \cite{Dick83_1, Carlson1990line}

>>>>

An often unavoidable consequence in electronic spectroscopy is broadened line shapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
In the discussion that follows, we assume that a ground state vibrational frequency, $\ket{g,v}$, experiences variations that are correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,\tilde{v}'}$ is $\omega_{e\tilde{v}'} + c\xi$, where c is a shift coefficient.
We assume the fluctuations controlling the frequency variations are slow (the static limit), so that homogeneous lineshapes are unaffected by this fluctuation. 
When both states positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
For simplicity, we consider only c = $\pm$1.
To simplify discussion below, we map $\Delta_{e\tilde{v}', gv} \rightarrow \Delta_{ba}$ and $\Delta_{g0,gv} \rightarrow \Delta_{ga}$.

@@

Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details.} 
\begin{subequations}
\begin{equation}\label{linenarrowa}
	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)
\end{equation}
for correlated ($c = 1$) states and
\begin{equation}
	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
\end{equation}
\end{subequations}
for anti-correlated ($c = -1$) states.
The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
As such, the HDFG pathway considered in this work line-narrows correlated modes. 
These results are consistent with the idea that non-parametric, non-linear spectroscopies line-narrow correlated modes. \cite{Dick83_1, Carlson1990line}

### 2024-09-30 si.tex
first pass at fixing contour problems
pp 408 of Morse and feshbach

In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
The dependence of relevant Franck-Condon factors and Herzberg-Teller integrals on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
The products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A,B$ coefficents discussed in the main text are plotted in \autoref{fig:fcht_product}.

@@

\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
Recall that if a complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
\begin{subequations}\label{eq:generalcontour}
	\begin{equation}
		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \Res[f(z_k)]
	\end{equation}
where the residue of an n$^{\text{th}}$ order pole at $z = z_k$, $\Res[f(z_k)]$ is evaluated as
	\begin{equation}
		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k) \right]
	\end{equation}
For first order poles (the cases considered below), $n=1$, so that 
	\begin{equation}
		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
	\end{equation}
\end{subequations}
Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles.

\subsection{Anti-correlated Modes}
For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
Since \autoref{generalcontour} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
In other words, we can choose the contour which wraps around the least number of poles.
For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{generalcontour} in the upper half of the complex plane for the case of anti-correlated modes, as it contains the least number of poles.
Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
It is clear that no matter which contour is chosen, the contour will envelop two poles.
We choose to evaluate along the contour in the bottom half of the complex plane (see \autoref{fig:contours}b), where the poles are $\{-i\sigma, \Delta_{ga}\}$.
Since the $\xi_k$ are nondegenerate,
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} + \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi + i \sigma\right) \\ 
			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi - \Delta_{ga}\right)\\
			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}} \frac{1}{\Delta_{ba} - i\sigma} \right) - 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ga} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
			&= -\frac{\eta_{ijkl}}{\Delta_{ga} + i \sigma} \left(\frac{1}{\Delta_{ba} - i \sigma} + \frac{2i\sigma}{(\Delta_{ga} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
		\end{split}
	\end{equation}
\end{widetext}

>>>>

In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
The dependence of relevant Franck-Condon factors and Herzberg-Teller integrals on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
The products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A,B$ coefficients discussed in the main text are plotted in \autoref{fig:fcht_product}.

@@

\section{Evaluating impact of static inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
Recall that if an analytic, complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
\begin{subequations}\label{eq:generalcontour}
	\begin{equation}
		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \Res[f(z_k)]
	\end{equation}
where the residue of an n$^{\text{th}}$ order pole at $z = z_k$, $\Res[f(z_k)]$ is evaluated as
	\begin{equation}
		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k) \right]
	\end{equation}
For first order poles (the cases considered below), $n=1$, so that 
	\begin{equation}
		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
	\end{equation}
\end{subequations}
Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles. 
In the case where the integration is only needed along the real axis, the contour can be drawn as a semicircle in the positive half of the complex plane. \cite{MorseFeshbach}

\subsection{Anti-correlated Modes}
For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$
Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
We evaluate along the contour where the poles are $\{i\sigma, -\Delta_{ba}\}$.
Since the $\xi_k$ are nondegenerate,
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi - i \sigma\right) \\ 
			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow -\Delta_{ba}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi + \Delta_{ba}\right)\\
			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} + i\sigma} \right) + 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ba} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
			&= \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
		\end{split}
	\end{equation}
\end{widetext}
